% Created 2023-06-08 Thu 16:14
% Intended LaTeX compiler: pdflatex
\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% Use roboto and lato for fonts
\renewcommand{\familydefault}{\sfdefault}

% Change the colours if you want to
\RequirePackage{xcolor}
\definecolor{dracula-background}{HTML}{141d28}
\definecolor{dracula-background-secondary-alt}{HTML}{44475a}
\definecolor{dracula-background-secondary}{HTML}{1e1f29}
\definecolor{dracula-foreground}{HTML}{f8f8f2}
\definecolor{dracula-sidebar-background}{HTML}{233346}
\definecolor{dracula-green}{HTML}{50fa7b}
\definecolor{dracula-dark-green}{HTML}{b8bb26}
\definecolor{dracula-violet}{HTML}{bd93f9}
\definecolor{dracula-magenta}{HTML}{ff79c6}
\definecolor{dracula-orange}{HTML}{ffb86c}
\definecolor{dracula-cyan}{HTML}{8be9fd}
\definecolor{dracula-red}{HTML}{ff5555}
\definecolor{dracula-yellow}{HTML}{f1fa8c}
\definecolor{dracula-body-text}{HTML}{C3C3C3}
\definecolor{dracula-comment}{HTML}{6272a4}
\definecolor{dracula-page-links}{HTML}{C26EFF}
\definecolor{dracula-attributes-color}{HTML}{FFFF80}
\definecolor{dracula-external-links}{HTML}{7CE973}
\definecolor{dracula-links-hover}{HTML}{92FFFF}
\definecolor{dracula-hashtags}{HTML}{FFD17E}
\definecolor{dracula-italics-color}{HTML}{FF7EA2}
\definecolor{dracula-bold-color}{HTML}{FF4E4E}
\definecolor{dracula-highlight-text-color}{HTML}{47405E}
\definecolor{dracula-highlighter}{HTML}{FFFF80}
\definecolor{dracula-sidebar-text}{HTML}{F2F2F2}
\definecolor{dracula-page-heading}{HTML}{FFBE49}
\definecolor{dracula-daily-heading}{HTML}{FFCA6A}
\definecolor{dracula-headings}{HTML}{F2F2F2}
\definecolor{dracula-bullets}{HTML}{7A6DAA}
\definecolor{dracula-closed-bullets}{HTML}{3E445D}
\definecolor{dracula-references}{HTML}{9E8DDB}
\definecolor{dracula-block-reference-text}{HTML}{FF9580}
\definecolor{dracula-namespaces}{HTML}{5EB9FF}
\definecolor{dracula-all-pages-mentions}{HTML}{FF9580}
\definecolor{dracula-cursor}{HTML}{F2F2F2}
\definecolor{dracula-icons}{HTML}{FBCC77}
\definecolor{dracula-icons-hover}{HTML}{81FFEA}
\definecolor{dracula-filter-icon}{HTML}{C26EFF}
\pagecolor{white}
\colorlet{name}{dracula-violet}
\colorlet{tagline}{dracula-comment}
\colorlet{heading}{dracula-namespaces}
\colorlet{headingrule}{dracula-bullets}
\colorlet{subheading}{dracula-orange}
\colorlet{accent}{dracula-page-links}
\colorlet{emphasis}{dracula-comment}
\colorlet{body}{dracula-background}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

\usepackage[rm]{roboto}
\usepackage[defaultsans]{lato}
\usepackage{paracol}
\columnratio{0.6} % Set the left/right column width ratio to 6:4.
\usepackage{luatexja}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fontawesome5}
\usepackage{fontmfizz}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[bottom]{footmisc}
\author{Daniel Otto Daniel Otto}
\date{\today}
\title{Data Analyst}
\begin{document}


\name{Daniel Otto}
% \photoR{2.8cm}{aidan_portrait.jpeg}
\tagline{Data Analyst}

\personalinfo{
  \homepage{www.danielotto.jp}
  \email{analytics@danielotto.jp}
  \phone{+81 80 7650 1991}
  \location{Tokyo, Japan}
  \github{nanjigen}
  \linkedin{dmotto}
  \dob{1991/10/18}
}
\makecvheader

​\begin{paracol}{2}

\cvsection{Experience}
\label{sec:org67ee2c3}
\cvevent{English Teacher}{ KDI}{ March 2023 -- Ongoing}{ Tokyo, Japan}
Teaching position at a well known bilingual Yochien, where I continue providing linguistics expertise in teaching strategies aimed at children. Also provided interpretation for monolingual co-workers on part of Japanese management.
\par\divider
\cvevent{English Teacher}{ NOVA}{ April 2022 -- March 2023}{ Tokyo, Japan}
Plied my understanding of linguistics and specialisation in second language acquisition teaching English to Japanese nationals.
\par\divider
\cvevent{Freelance translator}{ self-employed}{ Sept 2020 -- Ongoing}{ Tokyo, Sydney}
Variously residing between Japan and Australia working on Japanese to English game localisation and linguistic quality assurance over both mobile and console titles.
\par\divider
\cvevent{Lead Audio-Visual Technician}{ Showtime Productions}{ Nov 2016 -- Feb 2022}{ Sydney}
Lead technician operating across several convention centers - planning, setup, and execution of audio-visual requirements for conferences, trade shows, and special events; accommodating up to 1,500 attendees. Collaborated closely with event organizers, presenters, and clients to understand their audio-visual needs and provide tailored solutions, often giving stage direction and stage presence coaching.

\cvsection{Projects}
\label{sec:orgd006724}
\cvevent{Capstone Project}{ Coursera}{ 2023/02 -- Now}{ Tokyo, Japan}
\begin{itemize}
\item Capstone project for the completion of the Google Data Analytics Professional Certificate. Utilized tools such as \texttt{Beautifulsoup4} in order to scrape the SUUMO real estate website and analyze the results. \texttt{Pandas} was used for data cleaning and loading into a \texttt{sqlite} database, and with \texttt{bs4} and the \texttt{Pandas.Dataframe.pipe} method an ETL pipeline was established. Data was then extracted from the database and analysis was performed with an eye towards producing an interactive \texttt{Plotly/Dash} dashboard website. Viewable \href{https://github.com/nanjigen/tokyo-rentals-analysis}{here}.
\end{itemize}
\cvevent{Honours Thesis}{ UNSW}{ 2018 - 2020}{ Sydney, Australia}
\begin{itemize}
\item Analysed the JAWL (Japanese Academic Word List) in order to characterize the database and generate Flashcards for use in an eye-tracking learning intervention on L2 learners of Japanese in a university setting. \texttt{openpyxl} was used to extract data from the \texttt{.xlsx} file into a \texttt{pandas} dataframe. \texttt{NLTK} was used for P.O.S. tagging. Notebook available on request.
\end{itemize}

\cvsection{Volunteering}
\label{sec:org80528e7}
\cvevent{EVO Japan}{ EVO}{ 2018}{ Tokyo, Japan}
\cvevent{Various Japan Film Festivals}{ Japan Foundation}{ 2013 -- 2017}{ Australia}
In Australia
\switchcolumn

\cvsection{Languages}
\label{sec:orga49024e}
% \cvsection{Languages}

\cvskill{English - Native}{5}
% \divider

\cvskill{Japanese - JLPT N2}{4}
% \divider

% \cvskill{German}{3}

% %% Yeah I didn't spend too much time making all the
% %% spacing consistent... sorry. Use \smallskip, \medskip,
% %% \bigskip, \vpsace etc to make ajustments.
% \medskip
\cvsection{Education}
\label{sec:orgaa5b6da}
\cvevent{Google\ Data Analytics Professional Certificate}{ Coursera}{ March 2023 - ongoing}{}
Undertaking the Google Data Analytics Professional Certificate with Coursera, completing the capstone project and bringing my skills inline with industry standards.
\par\divider
\cvevent{Honours\ in Linguistics}{ University of New South Wales}{ Sept 2018 - 2020}{}
Performed eye-tracking research with human participants, studying the effect of various types of flashcard formatting on the acquisition of academic terms in a second language. I made use of Python to motivate data use, analyse results of captured data and featured these in my thesis and a Jupyter-notebook.
\par\divider
\cvevent{BA\ in Linguistics and Japanese Studies}{ University of New South Wales}{ 2013 - 2017}{}
Majored in Linguistics and Japanese Studies. This included the study of Japanese and Japanese history and culture. The Linguistics studies focused on pragmatics, semantics, syntactic and morphemic analysis and phonology. Courses were also done in psycholinguistics and second language acquisition.

\cvsection{Technical Skills}
\label{sec:org1052e65}
\begin{itemize}
\item Software
\end{itemize}
\cvtag{\faLinux GNU/Linux}
\cvtag{\mfChart Tableau}
\cvtag{\faEmacs Emacs}
\cvtag{Guix}
\cvtag{\mfVim Vim}
\begin{itemize}
\item Programming
\end{itemize}
\cvtag{\faNotebook Jupyter}
\cvtag{\mfPython Python}
\cvtag{\faRProject R}
\cvtag{\faDatabase SQL}
\cvtag{\mfClojure Clojure}
\cvtag{\mfShell BASH}
\cvtag{\LaTeX}

\end{paracol}
\end{document}